Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2016-07-08 manuscript/manuscript_pve.Rmd
improved RMD knitting with make pdfs and preload scripts

\
Word counts
\
Main text:
\
Summary: 200
\
Introduction:
\
Materials and methods:
\
Results:
\
Discussion:
\
Acknowledgements: 30
\
6 figures (5 color), 3 tables
\
Supporting information: 1 table

@@

```{r install packages, echo=FALSE, message=FALSE, warning=FALSE,results="hide"}
#install packages if not already installed
.packages = c("RColorBrewer", "doBy", "sciplot", "plyr","nlme", "multcomp", "plantecophys", "scales","smatr","plotrix",
                           "lme4", "lmerTest", "broom", "reporttools", "visreg", "pixiedust", "lubridate", "reshape",
              "magicaxis", "effects")

# Install CRAN packages (if not already installed)
.inst <- .packages %in% installed.packages()
if(length(.packages[!.inst]) > 0) install.packages(.packages[!.inst], repos = "http://cran.at.r-project.org")

# Load packages into session
lapply(.packages, library, character.only=TRUE)

```{r global data/sourcing, echo=FALSE, message=FALSE, warning=FALSE}
# Set Flag to include figures in text or not.
includeFigs <- TRUE

source("functions and packages/startscripts.R")
source("functions and packages/gamplotfunctions.R")

#table data
table1 <- read.csv("master_scripts/pve_table1.csv")
table2 <- read.csv("master_scripts/root_table.csv")
table3 <- read.csv("master_scripts/pve_table2.csv")
modeltable <- read.csv("master_scripts/modeltable.csv")

@@

*make sure this is correct, add CUE bit *
We then used this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.  Cumulative net leaf C gain for each treatment was equal to the sum of each value of *P* over 120 days and final seedling C was assumed to equal half of the final dry mass for observed seedlings.

>>>>

\
Word counts
\
Main text:
\
Summary: 200
\
Introduction:
\
Materials and methods:
\
Results:
\
Discussion:
\
Acknowledgements: 30
\
6 figures (5 color), 3 tables

@@

```{r global data/sourcing, echo=FALSE, message=FALSE, warning=FALSE}
# Set Flag to include figures in text or not.
includeFigs <- TRUE
```

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

source("manuscri[t/manuscript_preload.R")

# Make figure PDFs.
source("manuscript/make_figures.R")

@@

*make sure this is correct, add CUE bit*
We then used this model to test the hypothesis that the effects of belowground sink limitation on rates of leaf *A*~n~ were sufficient to accurately predict overall seedling biomass production after 120 days.  Cumulative net leaf C gain for each treatment was equal to the sum of each value of *P* over 120 days and final seedling C was assumed to equal half of the final dry mass for observed seedlings.
